---
title: "ProblemSet2"
author: "Anna"
date: "10/30/2022"
output: html_document
---

To set things up, I need to clear R's brain and add the necessary packages to my library.
```{r}
rm(list=ls()) # Clears R's brain
library(dplyr)
library(ggplot2)
library(here)
```

Importing the data:
```{r}
DF <- read.csv(here("Data", "Halloween_data_PS2.csv"))
# Using the here() function helps prevent the file path from breaking
glimpse(DF)
# After importing the data, it is good to look at the structure and type of data present
```

After glimpsing at the data, I see that the Costume and Type variables are "chr" (character) data, so I want to convert those into factor data:
```{r}
DF$Costume <- as.factor(DF$Costume)
DF$Type <- as.factor(DF$Type)
# Now that I converted these to factor data, I want to observe the data frame to ensure that they were in fact converted correctly. 
glimpse(DF)
str(DF)
# Either of these functions are good ways to see a summary of the data in the data frame. Both show that Costume and Type are now factors
```

Now that my data is imported, I want to check it for any errors. The first thing I see while looking at the data is that there are inconsistencies in how the Costume names were entered. Let's fix that!
```{r}
unique(DF$Costume) # this function shows me that some of the costumes are repeated and are considered unique strings within the Costume variable

wonder_woman <- which(DF$Costume == "wonder woman" | DF$Costume == "Wonder Woman" | DF$Costume == "Wonder woman")
DF$Costume[wonder_woman] <- "Wonder Woman"

clown <- which(DF$Costume == "creepy clown" | DF$Costume == "clown" | DF$Costume == "Creepy clown")
DF$Costume[clown] <- "clown"

witch <- which(DF$Costume == "Witch" | DF$Costume == "witch" | DF$Costume == "witch ")
DF$Costume[witch] <- "witch"
# 'witch' is included twice in this list because in the original .csv file, there is a 'witch ' with a space after it, making it a different string factor from just 'witch'
```

There is also an inconsistency in the Type variable because "Scary" and "scary" are considered unique strings. Let's fix this too!
```{r}
scary <- which(DF$Type == "Scary" | DF$Type == "scary" | DF$Type == "scary ")
DF$Type[scary] <- "Scary"
# 'scary' and 'scary ' are both included due to the same spacing problem in the .csv file as the 'witch' and 'witch ' scenario
```

Now that the data has been fixed, I can create Figures 1-3. 

Matching Fig. 1 - Here I am using piping to calculate the mean age and mean candy taken base on Costume and Type. First, I made a new data frame called 'fig1' to save the data...
```{r}
fig1 <- DF %>%
group_by(Costume, Type) %>%
  summarise(
    mean_age = mean(age, na.rm =T),
    mean_candy = mean(candy_pieces, na.rm = T))
```
... and then I used this new data frame to create a scatterplot
```{r}
ggplot(fig1, aes(x = mean_age, y = mean_candy, color = Type)) +
  geom_point(size = 2) +
  xlab("Mean age of kid (years)") +
  ylab("Mean number pieces taken") +
  theme_bw()
```

Matching Fig. 2 - First, I am creating a new data frame to isolate ages 10 years and under and costumes considered "Not scary"...
```{r}
fig2 <- DF %>%
group_by(Type = "Not scary") %>%
filter(age <= 10)

```
... and with this new data frame I can create a histogram.
```{r}
ggplot(fig2, aes(x = age)) +
  geom_histogram(bins = 4) + 
  xlab("Age of child") +
  ylab("Number")
```

Matching Fig. 3 - To create this boxplot, I am using the age and Costume data from the original data frame. 
```{r}
ggplot(DF, aes(x = age, y = Costume)) +
  geom_boxplot() +
  geom_point(size = 4, color = 'grey', alpha = 0.5) +
  xlab("Child age (years)") +
  ylab("Costume choice") +
  facet_wrap(~Type) # This allows me to group the data on the figure base don Type of costume

# I did not use 'coord_flip()' as recommended by the instructions because the coordinates were already correctly displayed (years on the x-axis, costumes on the y-axis)
```

